Verifying Demonstrations

### 2020-03-13 paper/ZKPK-instantiations.tex

\section{Instantiations of the \acs{ZKPK} protocols}%
\label{ZKPK-instantiations}

Following is a brief summary from~\cite{Camenisch-phdthesis} of how to 
instantiate general \acp{ZKPK} for discrete logarithms based on the Schnorr 
identification scheme~\cite{Schnorr}, which, in its original form, can be 
written as \(\PK[\alpha][A = g^\alpha]\).
The generalized form would be \[
  \PK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}].
\]
This could equivalently be written as
\begin{equation*}
  \Proto%
  {\PKprove[\{g_i\}_i, q, A, \{\alpha_i\}_i]}%
  {\PKverify[\{g_i\}_i, q, A]},
\end{equation*}
where \(\PKprove\) is run by the prover and \(\PKverify\) is run by the 
verifier.
\(\PKverify\) outputs accept (\(\top\)) or reject (\(\bot\)).
We give an instance of \(\PKprove\) and \(\PKverify\) in \cref{PKalgorithms}.
We also note that
\begin{multline*}
  \PK[\alpha, \beta][A = g^\alpha \land B = g^\beta] = \\
  \PK[\alpha][A = g^\alpha] \land \PK[\beta][B = g^\beta],
\end{multline*}
however, the challenge \(c\) must be the same in both sub-protocols.

>>>>

\paragraph*{Instantiations of the \acs{ZKPK} protocols}

For the convenience of the reader, we summarize 
(from~\cite{Camenisch-phdthesis}) how to instantiate general \acp{ZKPK} for 
discrete logarithms based on the Schnorr identification scheme~\cite{Schnorr}, 
which, in its original form, can be written as \(\PK[\alpha][A = g^\alpha]\).
The generalized form would be \[
  \PK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}].
\]
This could equivalently be written as
\begin{equation*}
  \Proto%
  {\PKprove[\{g_i\}_i, q, A, \{\alpha_i\}_i]}%
  {\PKverify[\{g_i\}_i, q, A]},
\end{equation*}
where \(\PKprove\) is run by the prover and \(\PKverify\) is run by the 
verifier.
\(\PKverify\) outputs accept (\(\top\)) or reject (\(\bot\)).
We give an instance of \(\PKprove\) and \(\PKverify\) in \cref{PKalgorithms}.
We also note that
\begin{multline*}
  \PK[\alpha, \beta][A = g^\alpha \land B = g^\beta] = \\
  \PK[\alpha][A = g^\alpha] \land \PK[\beta][B = g^\beta],
\end{multline*}
however, the challenge \(c\) must be the same in both sub-protocols.

### 2020-03-13 paper/formal-verification.tex
Adds formal verification section to outline

\section{Formal Verification}

@@

The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices we made. 
It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.

Tamarin's auto-prover validated the soundness and correctness
properties (in negligible computation time) and proved the security
properties used in~\cite{TamarinDB}. In the meantime,
\textcite{TamarinDBTF} introduced the notion of post-collusion
security which enabled them to prove \ac{DBTF}. In future work, we
will use this extension on our protocol.

>>>>

\section{Formal Verification}\label{formal-verification}

@@

The Tamarin code we wrote\footnote{provided in \url{https://doi.org/10.5281/zenodo.3709442}}%, with a short discussion of the modeling choices we made. 
 contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.

Tamarin's auto-prover validated the soundness and correctness
properties (in negligible computation time) and proved the security
properties used in~\cite{TamarinDB} and
\textcite{TamarinDBTF}. The latter introduced the notion of post-collusion
security which enabled them to prove \ac{DBTF}.

Note that proofs of formal verification are always limited by how well the specification captures reality. The abstraction does not capture the details of the bit-by-bit version that prevent \ac{DBTF} resistance.
